Re-fit

### 2023-01-15 scripts/r/04_refit/refit_sc.Rmd
🐛 - remove code for model that was excluded

# Team also had interaction effect_cat:Condition which leads to convergence issues
# since typ:AF = 0 and atyp:ANF = 0
neosilurus_omanensis_3_f0varrat_cat <- brm(
  PitchVariationRatioAtoU ~ effect_cat + Condition + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_3_f0varrat_cat",
  seed = my_seed
)

>>>>

# Team also had interaction effect_cat:Condition which leads to convergence issues
# since typ:AF = 0 and atyp:ANF = 0
# neosilurus_omanensis_3_f0varrat_cat <- brm(
#   PitchVariationRatioAtoU ~ effect_cat + Condition + (1|Participant) + (1|Adjective),
#   data = msa_data,
#   cores = 4,
#   threads = threading(2, grainsize = 100), 
#   backend = "cmdstanr",
#   file = "data/analyses/models/neosilurus_omanensis_3_f0varrat_cat",
#   seed = my_seed
# )
